Revisions made to the paper \\ ``Two applications of logic programming to Coq''

### 2021-03-09 papers/types2020/revisions/cover.tex
almost done

From the implementation point of view, we have extended the kernel to
account for conversion: this allows us to do prolog search and
therefore PBT on Inductive definitions that mix deduction and
computation. We have also implemented some optimizations to the kernel
itself, as briefly mentioned in the conclusion. We have experimented
with adding Hints to the kernel via Coq-Elpi's \texttt{Accumulate DB}
and while this is doable, it is not particularly useful for the
intended application, namely PBT. What we're working on is modifying
the elaboration tactic of Sec 5, which already sees the local context,
to handle Hints and Inductive. However,  given the deadline, this
will be future work.

@@

We meant the latter alternative. This is now made explicit in the text.ù

\begin{verbatim}
It is mysterious why you choose to only use constructors: you
 never justify this restriction. There is also an hint that you
 can use the Hints that eauto uses, but this is not reflected in
 your code. How can it be?
\end{verbatim}
As anticipated before, it is immediate to add another ``decide'' rule
that picks up previously proven lemmas. That would be close to the
functionality of \texttt{Hint Resolve}, but does not literally uses
Coq's Hints facility. It is conceivable that we could write some glue
code to connect the two, but handling all the fairly sophistcated features of the Hint
mechanism is out of the scope of this paper.

@@

\begin{verbatim}
1. The paper is centered on the idea that it is possible to use
 Coq-elpi to construct tactics following the ideas from FPC, but
 it lacks a proper evaluation of the tactics to show its
 benefits. It would make for a stronger story to have a thorough
 evaluation with its competitors (eauto for the first tactic and
 QuickChick for the second), even in restricted scenarios.
\end{verbatim}
comment

@@

Well spotted: we had forgot the guard in the third clause of \texttt{insert}. The roof terms now reflects those evidence.

@@

>>>>

From the implementation point of view, we have extended the kernel to
account for conversion: this allows us to do prolog search and
therefore PBT on Inductive definitions that mix deduction and
computation. We have also implemented some optimizations to the kernel
itself, as briefly mentioned in the conclusion. We have experimented
with adding Hints to the kernel via Coq-Elpi's \texttt{Accumulate DB}
and while this is doable, it is not particularly useful for the
intended application, namely PBT. What we're working on is modifying
the elaboration tactic of Sec 5, which already sees the local context,
to handle Hints and Inductive. All the peices are in place, however,  given the deadline, this
will not be part of this submission.

@@

We meant the latter alternative. This is now made explicit in the text.

\begin{verbatim}
It is mysterious why you choose to only use constructors: you
 never justify this restriction. There is also an hint that you
 can use the Hints that eauto uses, but this is not reflected in
 your code. How can it be?
\end{verbatim}
As anticipated before, it is immediate to add another ``decide'' rule
that picks up previously proven lemmas. That would be close to the
functionality of \texttt{Hint Resolve}, but does not literally uses
Coq's Hints facility. It is feasable that to write some glue
code to connect the two, but handling all the fairly sophistcated features of the Hint
mechanism is out of the scope of this paper.

@@

\begin{verbatim}
1. The paper is centered on the idea that it is possible to use
 Coq-elpi to construct tactics following the ideas from FPC, but
 it lacks a proper evaluation of the tactics to show its
 benefits. It would make for a stronger story to have a thorough
 evaluation with its competitors (eauto for the first tactic and
 QuickChick for the second), even in restricted scenarios.
\end{verbatim}

We meant this paper to be a proof-of-concept rather than a system
paper. We are not in the position to carry out a ``thorough evaluation'' with
Coq's automation not with QuickChick, if not for the high-level, qualitative remarks we have made in the paper. [AM: add more if I do more about dependent terms]

@@

Well spotted: we had forgot the inequality guard in the third clause of
\texttt{insert}. The proof terms now reflects those evidence.

@@

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
